---
title: "Fluke MSE performance metrics"
author: "Gavin Fay"
date: "2022-06-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(ggdist)
```

## Read in the results objects

These were created with the `performance-metrics.R` script.

```{r}
metrics <- readRDS("all_results_distrib.rds")
median_metrics <- readRDS("all_results_medians.rds")
state_metrics <- readRDS("full_state_metrics.rds")
#metrics
#median_metrics
#state_metrics
```

- summary of state metrics

```{r}
nu_state <- state_metrics %>% 
  group_by(om, mp, metric, isim) %>% 
  summarize(value = diff(range(value)),
            .groups = "drop") %>% 
  filter(metric %in% c("keep_one","kept:released")) %>% 
  mutate(metric = case_when(
    metric == "keep_one" ~ "keep_one_range",
    metric == "kept:released" ~ "kept:rel_range",
    TRUE ~ metric
  )) %>% 
  I()
#nu_state

nu_state_medians <- nu_state %>% 
  group_by(om, mp, metric) %>% 
  summarize(value = median(value, na.rm=TRUE)) %>% 
  filter(metric %in% c("keep_one_range","kept:rel_range")) %>% 
  I()

state_medians <- state_metrics %>% 
  group_by(om, mp, state, metric) %>% 
  summarize(value = median(value, na.rm=TRUE)) %>% 
  I()


```


- calculate the relative metrics comparing medians

```{r}
median_metrics <- median_metrics %>% 
  ungroup() %>% 
  select(-isim) %>% 
  bind_rows(nu_state_medians) %>% 
  I()

mp1_medians <- median_metrics %>% 
  ungroup() %>% 
  filter(mp == "MP 1") %>% 
  select(-mp) %>% 
  rename("mp1_val" = value) %>% 
  I()
#mp1_medians

nu_medians <- median_metrics %>% 
  ungroup() %>% 
  left_join(mp1_medians) %>% 
  mutate(rel_value = value/mp1_val) %>% 
  I()
```

- proportion outperforming mp1


- create table of all final summary metrics

```{r}
summary_metrics <- nu_medians %>% 
  select(om, mp, metric, value) %>% 
  filter(metric %in% c("keep_one",
                       "cs_per_trip",
                       "trophy",
                       "not overfished",
                       "not overfishing",
                       "prop_female",
                       "change_cs"
                       )) %>% 
  I()

summary_rel_metrics <- nu_medians %>% 
  select(om, mp, metric, rel_value) %>% 
  filter(metric %in% c("kept per trip",
                       "keep_one",
                       "keep_one_range",
                       "kept:released",
                       "kept:rel_range",
                       "spawning biomass",
                       #relative # of releases per trip compared to mp1
                       "rec_removals",
                       "ntrips"
                       #sales/income/GDP compared to mp1
                       )) %>% 
  mutate(metric = case_when(
    metric == "kept per trip" ~ "kept_per_trip_mp1",
    metric == "keep_one" ~ "keep_one_mp1",
    metric == "kept:released" ~ "kept:rel_mp1",
    metric == "spawning biomass" ~ "ssb_mp1",
    metric == "rec_removals" ~ "rec_removals_mp1",
    metric == "ntrips" ~ "ntrips_mp1",
    metric == "keep_one_range" ~ "keep_one_range_mp1",
    metric == "kept:rel_range" ~ "kept:rel_range_mp1",
    TRUE ~ metric)) %>% 
  rename(value = rel_value) %>% 
  I()

summary_metrics <- summary_metrics %>%
  bind_rows(summary_rel_metrics) %>% 
  I()
#summary_metrics

```


### Metrics by OM & MP

```{r}
summary <- summary_metrics %>% 
  mutate(om = factor(om),
         om = fct_recode(om, "base" = "1","MRIP bias" = "2","shift" = "3")) %>% 
  group_by(mp, metric) %>% 
  mutate(val2 = value/max(value, na.rm=TRUE)) %>% 
  # filter(!metric %in% c("total catch", "expense", "cs_per_trip",
  #                       "mulen_keep",
  #                       "mulen_release",
  #                       "not overfished",
  #                       "prop_female")) %>% 
  ggplot() +
  aes(x = metric, y = val2, col = om, group = mp) +
  geom_point() +
  coord_flip() +
  facet_grid(~mp) +
  geom_hline(yintercept = 0, lty=2, alpha =0.5) +
  theme(legend.position = "bottom") +
        #axis.text.y = element_blank()) +
  guides(fill = guide_legend(nrow = 1))
summary

```


### metrics across MPs for all oms
```{r}
p2 <- summary_metrics %>% 
  mutate(om = factor(om),
         om = fct_recode(om, "base" = "1","MRIP bias" = "2","shift" = "3"),
         metric = factor(metric, levels = c("keep_one",
                                            "kept_per_trip_mp1",
                                            "cs_per_trip",
                                            "trophy",
                                            "keep_one_mp1",
                                            "keep_one_range_mp1",
                                            "kept:rel_mp1",
                                            "kept:rel_range_mp1",
                                            "not overfished",
                                            "not overfishing",
                                            "ssb_mp1",
                                            "rel_per_trip_mp1",
                                            "rec_removals_mp1",
                                            "prop_female",
                                            "ntrips_mp1",
                                            "change_cs"#,
                                            #"gdp_mp1"
                                            ))) %>% 
  #filter(om == 1) %>% 
  ggplot() +
  aes(x = mp, y = value, col = mp, shape = om) +
  #geom_boxplot(outlier.shape=NA) +
  geom_point() +
  geom_line(aes(x = mp, y = value, group = om), col = "gray") +
  geom_point() + 
  scale_color_brewer(type = "qual", palette = 2) +
  facet_wrap(~metric, scale = "free_y", drop = F) +
  ylab("") +
  xlab("") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_blank()) +
  labs(fill = "") +
  guides(col = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2))
p2
```

```{r}
do_state_bp <- function(state_metrics = NULL) {
  title_metric <- state_metrics$metric[1]
  state_bp <- state_metrics %>% 
    #filter(metric %in% c("change_cs")) %>%  #c("kept per trip")) %>% 
  ggplot() +
  aes(x = mp, y = value, fill = mp) +
  geom_boxplot(outlier.shape=NA) +
  scale_fill_brewer(type = "qual", palette = 2) +
  facet_wrap(~state, scale = "free_y") +
  #facet_wrap(~metric, scale = "free_y") +
  ylab("") +
  xlab("") +
  theme_bw() +
  #ylim(0,5e+06) +
  theme(legend.position = "bottom",
        axis.text.x = element_blank()) +
  labs(fill = "",
       title = title_metric) + #kept per trip") +
  guides(fill = guide_legend(nrow = 1))
  return(state_bp)
}

```


```{r}
state_bp <- state_metrics %>% 
  filter(om == 1) %>% 
  nest_by(metric,.keep = TRUE) %>% 
  mutate(bp = list(do_state_bp(data)))
```

### metrics by state (base om) {.tabset}
```{r, results = 'asis', echo = FALSE}
for (i in seq_along(state_bp$metric)){
  tmp <- state_bp$bp[[i]]
  cat("####", tmp$data$metric[1], " \n")
  print(tmp)
  cat(" \n\n")
  }
```

```{r}
state_bp <- state_metrics %>% 
  filter(om == 2) %>% 
  nest_by(metric,.keep = TRUE) %>% 
  mutate(bp = list(do_state_bp(data)))
```

### metrics by state (MRIP bias) {.tabset}
```{r, results = 'asis', echo = FALSE}
for (i in seq_along(state_bp$metric)){
  tmp <- state_bp$bp[[i]]
  cat("####", tmp$data$metric[1], " \n")
  print(tmp)
  cat(" \n\n")
  }
```

```{r}
state_bp <- state_metrics %>% 
  filter(om == 3) %>% 
  nest_by(metric,.keep = TRUE) %>% 
  mutate(bp = list(do_state_bp(data)))
```

### metrics by state (distribution shift) {.tabset}
```{r, results = 'asis', echo = FALSE}
for (i in seq_along(state_bp$metric)){
  tmp <- state_bp$bp[[i]]
  cat("####", tmp$data$metric[1], " \n")
  print(tmp)
  cat(" \n\n")
  }
```


### how many states do better than MP1?
```{r}
state_medians <- state_metrics %>% 
  group_by(om, mp, metric, state) %>% 
  summarize(value = median(value, na.rm=TRUE)) %>% 
  ungroup()

mp1 <- state_medians %>% 
  filter(mp == "MP 1") %>% 
  mutate(mp1_val = value) %>% 
  select(metric, mp1_val, om, state)
  
beat_mp1 <- state_medians %>% 
  #filter(mp != "MP 1") %>% 
  left_join(mp1) %>% 
  mutate(beat_mp1 = ifelse(value > mp1_val, 1,0)) %>% 
  group_by(om, mp, metric) %>% 
  summarize(nbeat = sum(beat_mp1, na.rm=TRUE))
beat_mp1

```

```{r}
nbeat_plot <- beat_mp1 %>% 
  mutate(om = factor(om),
         om = fct_recode(om, "base" = "1","MRIP bias" = "2","shift" = "3"),
         mp = fct_expand(mp,"MP 1"),
         mp = fct_relevel(mp, "MP 1")) %>% 
  ggplot() +
  aes(x = mp, y = nbeat, col = mp, shape = om) +
  #geom_boxplot(outlier.shape=NA) +
  geom_point() +
  geom_line(aes(x = mp, y = nbeat, group = om), col = "gray") +
  scale_color_brewer(type = "qual", palette = 2) +
  facet_wrap(~metric, drop = F) +
  ylab("") +
  xlab("") +
  ylim(0,10) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_blank()) +
  labs(fill = "") +
  guides(col = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2))
nbeat_plot
ggsave("outputs/plots/nstates_beat_mp1.png",nbeat_plot,width=9,height=5)
```


```{r}
mp1 <- state_metrics %>% 
  filter(mp == "MP 1") %>% 
  mutate(mp1_val = value) %>% 
  select(metric, mp1_val, om, isim, state)
  
beat_mp1 <- state_metrics %>% 
  filter(mp != "MP 1") %>% 
  left_join(mp1) %>% 
  mutate(beat_mp1 = ifelse(value > mp1_val, 1,0)) %>% 
  group_by(om, mp, metric, state) %>% 
  summarize(prop = mean(beat_mp1, na.rm=TRUE))

beat_mp1
  
  
```

