---
title: "Fluke MSE performance metrics"
author: "Gavin Fay"
date: "2022-07-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(ggdist)
library(scales)
library(fmsb)
```

#### Read in the results objects

These were created with the `performance-metrics.R` script.

```{r}
metrics <- readRDS("all_results_distrib.rds")
median_metrics <- readRDS("all_results_medians.rds")
#metrics <- readRDS("metrics.rds")
#median_metrics <- readRDS("median_metrics.rds")
state_metrics <- readRDS("full_state_metrics.rds")
#metrics
#median_metrics
#state_metrics
```

```{r}
# add radar plot
do_small_radar_plot <- function(metrics) {
  # metrics is a dataframe of metrics, expecting columns
  # metrics <- tibble(metric = rep(letters[1:5],each=3),
  #                   value = runif(15),
  #                   mp = as.character(rep(1:3,5)))
  # # metric 
  # # value
  # # mp (management procedure)
  summaries <- metrics %>% 
    group_by(metric) %>% 
    summarize(min = min(value, na.rm = TRUE),
              max = max(value, na.rm = TRUE)) %>% 
    #pivot_longer(cols = c(2:3),names_to = "mp",
    #             values_to = "value") %>% 
    #pivot_wider(names_from = metric, values_from = value) %>% 
    #arrange(desc(mp)) %>% 
    I()
  #summaries  
  nmetrics <- length(unique(metrics$metric))
  nmp <- length(unique(metrics$mp))
  
  d <- metrics %>% 
    group_by(mp) %>% 
    left_join(summaries) %>% 
    mutate(value = value/(max + 1e-08)) %>% 
    select(mp, metric, value) %>% 
    pivot_wider(names_from = metric, values_from = value) %>% 
    ungroup()
  
  bounds <- tibble(mp = c("max","min"),
                   #"spawning biomass" = c(1,0),
                   #"total catch" = c(1,0),
                   "kept:released" = c(1,0),
                   "kept per trip" = c(1,0),
                   "not overfishing" = c(1,0),
                   "not overfished" = c(1,0),
                   "change_cs" = c(1,0),
                   #"mulen_keep" = c(1,0),
                   #"mulen_release" = c(1,0),
                   #"trophy" = c(1,0),
                   #"rec_removals" = c(1,0),
                   "keep_one" = c(1,0)) #,
                   #"prop_female" = c(1,0),
                   #"ntrips" = c(1,0)) #,
  #filter(metric %in% c("change_cs", "kept per trip", "kept:released", "not overfished", "not overfishing")) %>% 
  #d = c(1,0),
  #e = c(1,0))
  
  dd <- bounds %>% 
    bind_rows(d)
  
  #NEW PLOT
  #colorblind colors
  colors_fill2<-c(alpha("#000000",0.1),
                  alpha("#E69F00",0.1),
                  alpha("#56B4E9",0.1),
                  alpha("#009E73",0.1),
                  alpha("#F0E442",0.1),
                  alpha("#E69F00",0.1),
                  alpha("#56B4E9",0.1),
                  alpha("#009E73",0.1))
  colors_line2<-c(alpha("#000000",0.9),
                  alpha("#E69F00",0.9),
                  alpha("#56B4E9",0.9),
                  alpha("#009E73",0.9),
                  alpha("#F0E442",0.9),
                  alpha("#E69F00",0.9),
                  alpha("#56B4E9",0.9),
                  alpha("#009E73",0.9))
  colors_line2<-c(alpha("#1b9e77",0.9),
                  alpha("#d95f02",0.9),
                  alpha("#56B4E9",0.9),
                  alpha("#dc14cf",0.9),
                  #alpha("#009E73",0.9),
                  alpha("#F0E442",0.9),
                  alpha("#E69F00",0.9),
                  alpha("#56B4E9",0.9),
                  alpha("#009E73",0.9))
  
  colors_fill2<-c(alpha("#1b9e77",0.1),
                  alpha("#d95f02",0.1),
                  alpha("#7570b3",0.1),
                  alpha("#e7298a",0.1),
                  alpha("#66a61e",0.1),
                  alpha("#e6ab02",0.1),
                  alpha("#a6761d",0.1),
                  alpha("#d95f02",0.1))
  
  colors_line2<-c(alpha("#1b9e77",0.9),
                  alpha("#d95f02",0.9),
                  alpha("#7570b3",0.9),
                  alpha("#e7298a",0.9),
                  alpha("#66a61e",0.9),
                  alpha("#e6ab02",0.9),
                  alpha("#a6761d",0.9),
                  alpha("#d95f02",0.9))
  
  #colorblind
  radarchart(dd[,-1],seg=5,pcol=colors_line2,
             pfcol=colors_fill2,plwd=2,
             vlabels=names(dd)[-1], vlcex=0.8,
             plty=c(rep(1,7),rep(2,7)),
             pdensity=0)
  rows<<-rownames(dd[-c(1,2),])
  colors_line<<-colors_line2
  legend("bottomright",inset=0,title ="",title.adj = 0.2,
         legend=unique(d$mp),
         pch=16,
         col=colors_line2[1:nmp],
         lty=1, cex=0.8, bty= 'n', y.intersp=1)
  
}

```


```{r}
nu_state <- state_metrics %>% 
  group_by(om, mp, metric, isim) %>% 
  summarize(value = diff(range(value)),
            .groups = "drop") %>% 
  filter(metric %in% c("keep_one","kept:released")) %>% 
  mutate(metric = case_when(
    metric == "keep_one" ~ "keep_one_range",
    metric == "kept:released" ~ "kept:rel_range",
    TRUE ~ metric
  )) %>% 
  I()
#nu_state

metrics <- metrics %>% 
  bind_rows(nu_state)

nu_state_medians <- nu_state %>% 
  group_by(om, mp, metric) %>% 
  summarize(value = median(value, na.rm=TRUE)) %>% 
  filter(metric %in% c("keep_one_range","kept:rel_range")) %>% 
  I()

state_medians <- state_metrics %>% 
  group_by(om, mp, state, metric) %>% 
  summarize(value = median(value, na.rm=TRUE)) %>% 
  I()


```


- calculate the relative metrics comparing medians

```{r}
median_metrics <- median_metrics %>% 
  ungroup() %>% 
  select(-isim) %>% 
  bind_rows(nu_state_medians) %>% 
  I()

mp1_medians <- median_metrics %>% 
  ungroup() %>% 
  filter(mp == "MP 1") %>% 
  select(-mp) %>% 
  rename("mp1_val" = value) %>% 
  I()
#mp1_medians

nu_medians <- median_metrics %>% 
  ungroup() %>% 
  left_join(mp1_medians) %>% 
  mutate(rel_value = value/mp1_val) %>% 
  I()
```
- calculate the relative metrics 

```{r}
mp1_metrics <- metrics %>% 
  ungroup() %>% 
  filter(mp == "MP 1") %>% 
  select(-mp) %>% 
  rename("mp1_val" = value) %>% 
  I()

nu_metrics <- metrics %>% 
  ungroup() %>% 
  left_join(mp1_metrics) %>% 
  mutate(rel_value = value/mp1_val) %>% 
  I()
```

- proportion outperforming mp1


- create table of all final summary metrics

```{r}
summary_metrics <- nu_medians %>% 
  select(om, mp, metric, value) %>% 
  filter(metric %in% c("keep_one",
                       "cs_per_trip",
                       "trophy",
                       "not overfished",
                       "not overfishing",
                       "prop_female",
                       "change_cs"
                       )) %>% 
  I()

summary_rel_metrics <- nu_medians %>% 
  select(om, mp, metric, rel_value) %>% 
  filter(metric %in% c("kept per trip",
                       "keep_one",
                       "keep_one_range",
                       "kept:released",
                       "kept:rel_range",
                       "spawning biomass",
                       #relative # of releases per trip compared to mp1
                       "rec_removals",
                       "ntrips"
                       #sales/income/GDP compared to mp1
                       )) %>% 
  mutate(metric = case_when(
    metric == "kept per trip" ~ "kept_per_trip_mp1",
    metric == "keep_one" ~ "keep_one_mp1",
    metric == "kept:released" ~ "kept:rel_mp1",
    metric == "spawning biomass" ~ "ssb_mp1",
    metric == "rec_removals" ~ "rec_removals_mp1",
    metric == "ntrips" ~ "ntrips_mp1",
    metric == "keep_one_range" ~ "keep_one_range_mp1",
    metric == "kept:rel_range" ~ "kept:rel_range_mp1",
    TRUE ~ metric)) %>% 
  rename(value = rel_value) %>% 
  I()

summary_metrics <- summary_metrics %>%
  bind_rows(summary_rel_metrics) %>% 
  I()
#summary_metrics

```

- create table of all final metrics

```{r}
metrics <- nu_metrics %>% 
  select(om, mp, metric, isim, value) %>% 
  filter(metric %in% c("keep_one",
                       "cs_per_trip",
                       "trophy",
                       "not overfished",
                       "not overfishing",
                       "prop_female",
                       "change_cs"
                       )) %>% 
  I()

rel_metrics <- nu_metrics %>% 
  select(om, mp, metric, isim, rel_value) %>% 
  filter(metric %in% c("kept per trip",
                       "keep_one",
                       "keep_one_range",
                       "kept:released",
                       "kept:rel_range",
                       "spawning biomass",
                       #relative # of releases per trip compared to mp1
                       "rec_removals",
                       "ntrips"
                       #sales/income/GDP compared to mp1
                       )) %>% 
  mutate(metric = case_when(
    metric == "kept per trip" ~ "kept_per_trip_mp1",
    metric == "keep_one" ~ "keep_one_mp1",
    metric == "kept:released" ~ "kept:rel_mp1",
    metric == "spawning biomass" ~ "ssb_mp1",
    metric == "rec_removals" ~ "rec_removals_mp1",
    metric == "ntrips" ~ "ntrips_mp1",
    metric == "keep_one_range" ~ "keep_one_range_mp1",
    metric == "kept:rel_range" ~ "kept:rel_range_mp1",
    TRUE ~ metric)) %>% 
  rename(value = rel_value) %>% 
  I()

metrics <- metrics %>%
  bind_rows(rel_metrics) %>% 
  I()
#summary_metrics

```

### Metrics by OM & MP

```{r}
summary <- summary_metrics %>% 
  mutate(om = factor(om),
         om = fct_recode(om, "base" = "1","MRIP bias" = "2","shift" = "3")) %>% 
  group_by(mp, metric) %>% 
  mutate(val2 = value/max(value, na.rm=TRUE)) %>% 
  # filter(!metric %in% c("total catch", "expense", "cs_per_trip",
  #                       "mulen_keep",
  #                       "mulen_release",
  #                       "not overfished",
  #                       "prop_female")) %>% 
  ggplot() +
  aes(x = metric, y = val2, col = om, group = mp) +
  geom_point() +
  coord_flip() +
  facet_grid(~mp) +
  geom_hline(yintercept = 0, lty=2, alpha =0.5) +
  theme(legend.position = "bottom") +
        #axis.text.y = element_blank()) +
  guides(fill = guide_legend(nrow = 1))
summary

```


### metrics across MPs for all oms
```{r}
p2 <- summary_metrics %>% 
  mutate(om = factor(om),
         om = fct_recode(om, "base" = "1","MRIP bias" = "2","shift" = "3"),
         mp2 = fct_recode(mp,
                          "status quo" = "MP 1",
                          "minsize-1" = "MP 2", 
                          "season" = "MP 3", 
                          "region" = "MP 4",
                          #"c1@14" = "MP 5", 
                          "c3@17" = "MP 6",
                          "c1@16-19" = "MP 7",
                          "slot" = "MP 8"),
         metric = factor(metric, levels = c("keep_one",
                                            "kept_per_trip_mp1",
                                            "cs_per_trip",
                                            "trophy",
                                            "keep_one_mp1",
                                            "keep_one_range_mp1",
                                            "kept:rel_mp1",
                                            "kept:rel_range_mp1",
                                            "not overfished",
                                            "not overfishing",
                                            "ssb_mp1",
                                            "rel_per_trip_mp1",
                                            "rec_removals_mp1",
                                            "prop_female",
                                            "ntrips_mp1",
                                            "change_cs"#,
                                            #"gdp_mp1"
                                            ))) %>% 
  #filter(om == 1) %>% 
  ggplot() +
  aes(x = mp2, y = value, col = mp2, shape = om) +
  #geom_boxplot(outlier.shape=NA) +
  geom_point() +
  geom_line(aes(x = mp2, y = value, group = om), col = "gray") +
  geom_point() + 
  scale_color_brewer(type = "qual", palette = 2) +
  facet_wrap(~metric, scale = "free_y", drop = F) +
  ylab("") +
  xlab("") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_blank()) +
  labs(fill = "",
       col = "") +
  guides(col = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2))
ggsave("outputs/plots/median-metrics-alloms-slides.png",p2,width=9,height=5)
p2
```

### Base Operating Model Scenario

```{r}
metrics2 <- metrics %>% 
  mutate(om = factor(om),
         om = fct_recode(om, "base" = "1","MRIP bias" = "2","shift" = "3"),
         mp2 = fct_recode(mp,
                          "status quo" = "MP 1",
                          "minsize-1" = "MP 2", 
                          "season" = "MP 3", 
                          "region" = "MP 4",
                          #"c1@14" = "MP 5", 
                          "c3@17" = "MP 6",
                          "c1@16-19" = "MP 7",
                          "slot" = "MP 8"),
         metric = factor(metric, levels = c("keep_one",
                                            "kept_per_trip_mp1",
                                            "cs_per_trip",
                                            "trophy",
                                            "keep_one_mp1",
                                            "keep_one_range_mp1",
                                            "kept:rel_mp1",
                                            "kept:rel_range_mp1",
                                            "not overfished",
                                            "not overfishing",
                                            "ssb_mp1",
                                            "rel_per_trip_mp1",
                                            "rec_removals_mp1",
                                            "prop_female",
                                            "ntrips_mp1",
                                            "change_cs"#,
                                            #"gdp_mp1"
                                            ))) 

```


```{r}
# add boxplots
p2 <- metrics2 %>% 
  filter(om == "base") %>% 
  ggplot() +
  aes(x = mp2, y = value, fill = mp2) +
  geom_boxplot(outlier.shape=NA) +
  scale_fill_brewer(type = "qual", palette = 2) +
  facet_wrap(~metric, scale = "free_y", drop = F) +
  ylab("") +
  xlab("") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_blank()) +
  labs(fill = "",
       subtitle = "Base scenario") +
  guides(fill = guide_legend(nrow = 1))
# add table summaries
#ggsave("boxplot-metrics.png",p2,width=8,height=8)
#ggsave("boxplot-metrics-om2.png",p2,width=8,height=8)
#ggsave("boxplot-metrics-om3.png",p2,width=8,height=8)
ggsave("outputs/plots/boxplot-metrics-om1-slides.png",p2,width=9,height=5)
p2
```

#### Tradeoffs among key metrics for the base operating model scenario
```{r}
# radar chart - not sure how to save this to file automagically
p3 <- median_metrics %>% 
  mutate(om = factor(om),
         om = fct_recode(om, "base" = "1","MRIP bias" = "2","shift" = "3")) %>% 
  filter(om == "base") %>% 
  mutate(mp = fct_recode(mp,
                   "status quo" = "MP 1",
                   "minsize-1" = "MP 2", 
                   "season" = "MP 3", 
                   "region" = "MP 4",
                   #"c1@14" = "MP 5", 
                   "3@17" = "MP 6",
                   "1@16-19" = "MP 7",
                   "slot" = "MP 8")) %>% 
  #filter(!metric %in% c("change_cs", "cs_per_trip")) %>% 
  #filter(!metric %in% c("expense","cs_per_trip","total catch")) %>% 
  filter(metric %in% c("change_cs", "kept per trip", "kept:released", "not overfished", "not overfishing", "keep_one")) %>% 
  do_small_radar_plot()

```

### MRIP bias Operating Model
```{r}
# add boxplots
p2 <- metrics2 %>% 
  filter(om == "MRIP bias") %>% 
  ggplot() +
  aes(x = mp2, y = value, fill = mp2) +
  geom_boxplot(outlier.shape=NA) +
  scale_fill_brewer(type = "qual", palette = 2) +
  facet_wrap(~metric, scale = "free_y", drop = F) +
  ylab("") +
  xlab("") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_blank()) +
  labs(fill = "",
       subtitle = "MRIP bias scenario") +
  guides(fill = guide_legend(nrow = 1))
# add table summaries
#ggsave("boxplot-metrics.png",p2,width=8,height=8)
#ggsave("boxplot-metrics-om2.png",p2,width=8,height=8)
#ggsave("boxplot-metrics-om3.png",p2,width=8,height=8)
ggsave("outputs/plots/boxplot-metrics-om2-slides.png",p2,width=9,height=5)
p2
```
#### Tradeoffs among key metrics for the MRIP bias operating model scenario
```{r}
# radar chart - not sure how to save this to file automagically
p3 <- median_metrics %>% 
    mutate(om = factor(om),
         om = fct_recode(om, "base" = "1","MRIP bias" = "2","shift" = "3")) %>% 
  filter(om == "MRIP bias") %>% 
  mutate(mp = fct_recode(mp,
                   "status quo" = "MP 1",
                   "minsize-1" = "MP 2", 
                   "season" = "MP 3", 
                   "region" = "MP 4",
                   #"c1@14" = "MP 5", 
                   "3@17" = "MP 6",
                   "1@16-19" = "MP 7",
                   "slot" = "MP 8")) %>% 
  #filter(!metric %in% c("change_cs", "cs_per_trip")) %>% 
  #filter(!metric %in% c("expense","cs_per_trip","total catch")) %>% 
  filter(metric %in% c("change_cs", "kept per trip", "kept:released", "not overfished", "not overfishing",
                       "keep_one")) %>% 
  do_small_radar_plot()

```


### Distribution Shift Operating Model
```{r}
# add boxplots
p2 <- metrics2 %>% 
  filter(om == "shift") %>% 
  ggplot() +
  aes(x = mp2, y = value, fill = mp2) +
  geom_boxplot(outlier.shape=NA) +
  scale_fill_brewer(type = "qual", palette = 2) +
  facet_wrap(~metric, scale = "free_y", drop = F) +
  ylab("") +
  xlab("") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_blank()) +
  labs(fill = "",
       subtitle = "Distribution shift scenario") +
  guides(fill = guide_legend(nrow = 1))
# add table summaries
#ggsave("boxplot-metrics.png",p2,width=8,height=8)
#ggsave("boxplot-metrics-om2.png",p2,width=8,height=8)
#ggsave("boxplot-metrics-om3.png",p2,width=8,height=8)
ggsave("outputs/plots/boxplot-metrics-om3-slides.png",p2,width=9,height=5)
p2
```
#### Tradeoffs among key metrics for the distribution shift operating model scenario
```{r}
# radar chart - not sure how to save this to file automagically
p3 <- median_metrics %>% 
    mutate(om = factor(om),
         om = fct_recode(om, "base" = "1","MRIP bias" = "2","shift" = "3")) %>% 
  filter(om == "shift") %>% 
  mutate(mp = fct_recode(mp,
                   "status quo" = "MP 1",
                   "minsize-1" = "MP 2", 
                   "season" = "MP 3", 
                   "region" = "MP 4",
                   #"c1@14" = "MP 5", 
                   "3@17" = "MP 6",
                   "1@16-19" = "MP 7",
                   "slot" = "MP 8")) %>% 
  #filter(!metric %in% c("change_cs", "cs_per_trip")) %>% 
  #filter(!metric %in% c("expense","cs_per_trip","total catch")) %>% 
  filter(metric %in% c("change_cs", "kept per trip", "kept:released", "not overfished", "not overfishing",
                       "keep_one")) %>% 
  do_small_radar_plot()

```


### State level metrics

```{r}
do_state_bp <- function(state_metrics = NULL) {
  title_metric <- state_metrics$metric[1]
  state_bp <- state_metrics %>% 
    #filter(metric %in% c("change_cs")) %>%  #c("kept per trip")) %>% 
  ggplot() +
  aes(x = mp, y = value, fill = mp) +
  geom_boxplot(outlier.shape=NA) +
  scale_fill_brewer(type = "qual", palette = 2) +
  facet_wrap(~state, scale = "free_y") +
  #facet_wrap(~metric, scale = "free_y") +
  ylab("") +
  xlab("") +
  theme_bw() +
  #ylim(0,5e+06) +
  theme(legend.position = "bottom",
        axis.text.x = element_blank()) +
  labs(fill = "",
       title = title_metric) + #kept per trip") +
  guides(fill = guide_legend(nrow = 1))
  return(state_bp)
}

```


<!-- #### State-by-state metrics for the Base Operating Model scenario -->
```{r}
state_bp <- state_metrics %>% 
  filter(om == 1) %>% 
   mutate(mp = fct_recode(mp,
                   "status quo" = "MP 1",
                   "minsize-1" = "MP 2", 
                   "season" = "MP 3", 
                   "region" = "MP 4",
                   #"c1@14" = "MP 5", 
                   "3@17" = "MP 6",
                   "1@16-19" = "MP 7",
                   "slot" = "MP 8")) %>% 
  nest_by(metric,.keep = TRUE) %>% 
  mutate(bp = list(do_state_bp(data)))
```

#### State-by-state metrics for the Base Operating Model scenario {.tabset}
```{r, results = 'asis', echo = FALSE}
for (i in seq_along(state_bp$metric)){
  tmp <- state_bp$bp[[i]]
  cat("####", tmp$data$metric[1], " \n")
  print(tmp)
  cat(" \n\n")
  }
```

```{r}
state_bp <- state_metrics %>% 
  filter(om == 2) %>% 
   mutate(mp = fct_recode(mp,
                   "status quo" = "MP 1",
                   "minsize-1" = "MP 2", 
                   "season" = "MP 3", 
                   "region" = "MP 4",
                   #"c1@14" = "MP 5", 
                   "3@17" = "MP 6",
                   "1@16-19" = "MP 7",
                   "slot" = "MP 8")) %>%   
  nest_by(metric,.keep = TRUE) %>% 
  mutate(bp = list(do_state_bp(data)))
```

#### State-by-state metrics for the MRIP Bias Operating Model scenario {.tabset}
```{r, results = 'asis', echo = FALSE}
for (i in seq_along(state_bp$metric)){
  tmp <- state_bp$bp[[i]]
  cat("####", tmp$data$metric[1], " \n")
  print(tmp)
  cat(" \n\n")
  }
```

```{r}
state_bp <- state_metrics %>% 
  filter(om == 3) %>% 
   mutate(mp = fct_recode(mp,
                   "status quo" = "MP 1",
                   "minsize-1" = "MP 2", 
                   "season" = "MP 3", 
                   "region" = "MP 4",
                   #"c1@14" = "MP 5", 
                   "3@17" = "MP 6",
                   "1@16-19" = "MP 7",
                   "slot" = "MP 8")) %>%   
  nest_by(metric,.keep = TRUE) %>% 
  mutate(bp = list(do_state_bp(data)))
```

#### State-by-state metrics for the Distribution Shift Operating Model scenario {.tabset}
```{r, results = 'asis', echo = FALSE}
for (i in seq_along(state_bp$metric)){
  tmp <- state_bp$bp[[i]]
  cat("####", tmp$data$metric[1], " \n")
  print(tmp)
  cat(" \n\n")
  }
```


#### How many states do better than the status quo management alternative?
```{r}
state_medians <- state_metrics %>% 
  group_by(om, mp, metric, state) %>% 
  summarize(value = median(value, na.rm=TRUE)) %>% 
  ungroup()

mp1 <- state_medians %>% 
  filter(mp == "MP 1") %>% 
  mutate(mp1_val = value) %>% 
  select(metric, mp1_val, om, state)
  
beat_mp1 <- state_medians %>% 
  #filter(mp != "MP 1") %>% 
  left_join(mp1) %>% 
  mutate(beat_mp1 = ifelse(value > mp1_val, 1,0)) %>% 
  group_by(om, mp, metric) %>% 
  summarize(nbeat = sum(beat_mp1, na.rm=TRUE))
beat_mp1

```

```{r}
nbeat_plot <- beat_mp1 %>% 
  mutate(om = factor(om),
         om = fct_recode(om, "base" = "1","MRIP bias" = "2","shift" = "3"),
         mp = fct_expand(mp,"MP 1"),
         mp = fct_relevel(mp, "MP 1")) %>% 
  ggplot() +
  aes(x = mp, y = nbeat, col = mp, shape = om) +
  #geom_boxplot(outlier.shape=NA) +
  geom_point() +
  geom_line(aes(x = mp, y = nbeat, group = om), col = "gray") +
  scale_color_brewer(type = "qual", palette = 2) +
  facet_wrap(~metric, drop = F) +
  ylab("") +
  xlab("") +
  ylim(0,10) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_blank()) +
  labs(fill = "") +
  guides(col = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2))
nbeat_plot
ggsave("outputs/plots/nstates_beat_mp1.png",nbeat_plot,width=9,height=5)
```


```{r}
mp1 <- state_metrics %>% 
  filter(mp == "MP 1") %>% 
  mutate(mp1_val = value) %>% 
  select(metric, mp1_val, om, isim, state)
  
beat_mp1 <- state_metrics %>% 
  filter(mp != "MP 1") %>% 
  left_join(mp1) %>% 
  mutate(beat_mp1 = ifelse(value > mp1_val, 1,0)) %>% 
  group_by(om, mp, metric, state) %>% 
  summarize(prop = mean(beat_mp1, na.rm=TRUE))

beat_mp1
  
  
```

